Figures

### 2019-05-06 manuscript/figures.Rmd
specify 1 to 1 line

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```

>>>>

```{r nlcd-versus-cdl, fig.cap = "Comparison between NLCD (2011) derived and CDL (2010) derived total watershed ag and watershed pasture cover. Line is 1:1 not regression.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/04_nlcd-versus-cdl-1.pdf")
```
